Double White Dwarf Mergers with CASTRO\\ I. Methodology and Code Verification

### 2013-05-11 paper.tex
change to default

This change can be used in the public version of Castro by setting
{\tt castro.ppm\_reference = 1}.  Figure~\ref{Fig:sod} shows the
solution to the Sod problem using the old and new reference states.
We see that the shock and contact are slightly sharper with this new
reference state, but also there is a slight dip at the tail of the
rarefaction with the new method.

@@

To properly describe the gravitational potential for the system, we need 
isolated boundary conditions.  The adaptive gravity solve in Castro 
is described in \cite{castro}, and consists of both level and composite
solves, and a final synchronization at the end.  To implement isolated
boundary conditions, we make the simplying assumption that only level
0 grids will touch the boundary of our computational domain.

>>>>

This change is now the default in the public version of Castro.
Figure~\ref{Fig:sod} shows the
solution to the Sod problem using the old and new reference states.
We see that the shock and contact are slightly sharper with this new
reference state, but also there is a slight dip at the tail of the
rarefaction with the new method.

@@

To properly describe the gravitational potential for the system, we need 
isolated boundary conditions.
